---
title: "DATA 607 - Week 9 Assignment"
author: "Rob Welk"
date: "March 31, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Problem Statement
API's are a convienient way of obtaining data from the web without the use of scraping techniques.  In this assingment, data is pulled from the New York Times API, and is stored in R as a dataframe. The most viewed articles from the week starting March 24, 2019 will be pulled.

# Packages Used
```{r, message=FALSE}
library(jsonlite)
library(dplyr)
library(magrittr)
library(ggplot2)
```

# API data into R, 
the jsonlite package makes it easy to get the data into R. 

```{r}
# url obtained from https://developer.nytimes.com/docs/most-popular-product/1/overview
url <- "https://api.nytimes.com/svc/mostpopular/v2/viewed/1.json?q=&facet_filter=true&api-key=UqvZ79vy3AyYhFwEMTHCT9mpyzlC6GPp"

# the fromJSON function will return a nested list - the flatten parameter will allow for a dataframe structure to be used
NYT.mostviewed <- fromJSON(url, flatten=T) %>% data.frame()                 
```

# Tidy and Visualize
The returned dataframe can be tidied.  Variables of interest were selected and renamed to provide a more concise table. Finally a barplot showing which sections the most viewed articles belong to is included

```{r}
#Select metadata variables of interest.  The url of the articles, section, author, title, date, and view rank are selected.
NYT.mostviewed %<>%  select(link='results.url',
                                  section='results.section', 
                                  author='results.byline',
                                  title='results.title',
                                  published_date='results.published_date', 
                                  view_rank='results.views')

ggplot(NYT.mostviewed,aes(section)) + geom_bar() +
                                      coord_flip()
                              

# Information on the most viewed artical of the week.
NYT.mostviewed %>% filter(view_rank==1)
```
 